### 2014-04-12 doc/uist14/intro.tex
finished pass over intro and related work; folded background into rel. work

The imprecision of human head movement suggests adapting area cursor techniques known from assistive devices~\cite{kabbash1995prince,worden1997making,Findlater-uist2010}. Such techniques employ a two-step selection process: {\em coarse} selection of an area of interest, followed by {\em refinement} to select a target within that region.

>>>>

The imprecision of human head movement suggests adapting area cursor techniques known from assistive devices~\cite{kabbash1995prince,worden1997making,findlater2010enhanced}. Such techniques employ a two-step selection process: {\em coarse} selection of an area of interest, followed by {\em refinement} to select a target within that region.
